\section{Methodology}
In this section you should describe the method of the experiment.



\subsection{Hardware}
The experiments conducted in this report were performed on a computer with the following specifications:
\begin{itemize}
	\item CPU: i5-2500 (4 cores @ 3.3-3.7	GHz)
	\item RAM: 8 GB DDR3
	\item OS:  Ubuntu 15.04
\end{itemize}

\subsection{Introductory Experiments}
To breed foster familiarity with Octave, a task was issued that involved generating a .wav file with a given method, and then creating one for comparison. The difference between the two functions being that the first one relies on a single call to rand() to generate multiple values, while the new method makes a call to rand() for each value in turn. A sample rate of 8000Hz was used, to decrease computation time. 

The given implementation took 173ms to generate 1000s of 8000Hz white noise. The custom implementation took 64244ms. This new method is a handy 370 times slower than the original method. This speed-down is likely due to the overheads of calling the rand() function multiple times.

The code for the custom implementation is shown below:

\begin{Matlab}
function whiten = createwhiten(s)
  sample_rate = 8000;
  whiten = zeros(s*sample_rate,1);
  t = s*sample_rate
  for i = 1:t
    whiten(i) = rand();
  end
  
  whiten = whiten*2-1;
end
\end{Matlab}


\subsection{Correlation Implementation}
The source code for the bespoke correlation solution is shown below.

\begin{Matlab}
function r = mycorr(x,y)
	% readability >> succinctness
	sx  = sum(x);
	sy  = sum(y);
	sxy = sum(x.*y);    % elementwise multiplication
	sx2 = sum(x.^2);    % elementwise squares
	sy2 = sum(y.^2);
	n   = max(size(x)); % just in case we get some column/row vector mixups
	num = sxy - sx*sy/n;
	den = sqrt((sx2-(sx.^2)/n)*(sy2-(sy.^2)/n));
	r = -2; % default, in case correlation could not be performed
	if(den != 0)
		r = num/den;
	end
end
\end{Matlab}

  
\subsection{Experiment Procedure}
Furthermore, include detail relating to the experiment itself: what did you do, in what order was this done, why was this done, etc.  What are you trying to prove / disprove?